Miniproject - Analytic Number Theory

### 2021-12-20 Analytic number theory/submission.tex
Use candidate number instead of student number
Finalized ANT

\title{Miniproject - Analytic Number Theory}
\author{Student Number: 1462479}
\date{19.12.2021}

@@

    Note that property (ii) and (iii) directly follow from the definition, as $\chi_f(n)$ only depends on the value of $n$ modulo $q$.
    So consider some $a, b \in \N$.
    If both $a \perp q$ and $b \perp q$ then
    \begin{equation*}
        \chi_f(a)\chi_f(b) = \chi([a])\chi([b]) = \chi([ab]) = \chi_f(ab)
    \end{equation*}
    as also $ab \perp q$.

@@

        \sum_{1 \leq n \leq X} \left| \chi(n) n^{-s} \right| \leq \sum_{1 \leq n \leq X} C \left| n^{-s} \right| \leq C \sum_{1 \leq n \leq X} \left| n^{-s} \right|

@@

        &\geq \sum_{n \geq 0} \ \sum_{0 < k \leq q}\sgn(c) \chi(qn + k) (qn + n)^{-s} \\
        &= \sum_{n \geq 0} \sgn(c) (qn + n)^{-s} \underbrace{\sum_{0 < k \leq q} \chi(qn + k)}_{= c} \\
        &\geq \frac {|c|} {(q + 1)^s} \sum_{n \geq 1} n^{-s} = \frac {|c|} {(q + 1)^s} \zeta(s)

@@

        &\leq (qn)^s \frac {sk(qn)^{-1}} {(q^2n^2 + qnk)^s} = \frac {sk} {qn(qn + k)^s} = O(sn^{-s - 1})

@@

    If $s > 1$ and $k \leq q$, then also $(qn)^{-s} - (qn + k)^{-s} = O(sn^{-(1 + \epsilon)})$ for some small enough $0 < \epsilon < 1$.

@@

        =& \ O(qCX^{-s} + qCY^{-s}) + \sum_{X/q \leq n \leq Y/q} \ \sum_{0 < k \leq q} \chi(qn + k) \Bigl( (qn)^{-s} + \underbrace{(qn + k)^{-s} - (qn)^{-s}}_{= O(sn^{-(1 + \epsilon)})} \Bigr) \\
        =& \ O(qCX^{-s}) + \sum_{X/q \leq n \leq Y/q} \Bigl( (qn)^{-s} c + \sum_{0 < k \leq q} O(Csn^{-(1 + \epsilon)}) \Bigr) = \\
        =& \ O(qCX^{-s}) + 0 + O\Bigl( Cqs \sum_{X/q \leq n \leq Y/q} n^{-(1 + \epsilon)} \Bigr) \\
        =& \ O(qCX^{-s}) + O\Bigl( Cqs \sum_{n \geq X/q} n^{-(1 + \epsilon)} \Bigr)

@@

    Thus the limit is continuous and extends $L(s, \chi_f)$ defined on $]1, \infty[$.
    It follows that $\lim_{t \to s^+} L(t, \chi_f)$ exists and is equal to $\sum_{n \geq 1} \chi(n) n^{-s}$.

@@

        \log(1 - x) = -x + O(x^2)

@@

    as by Taylor series expansion, find

@@

    Now consider the element $\alpha = \omega_q - xqP \in \mathcal{O}$. Then
    \begin{align*}
        N_{K/\Q}(\alpha) &= \prod_{\sigma: K \to \C \ \text{$\Q$-field homomorphism}} \sigma(\omega_q - xqP) \\
        &= \prod_{\sigma} (\sigma(\omega_q) - xqP) = \mathrm{MiPo}_\Q(\omega_q)(xqP) = \Phi_q(xqP) \neq 1
    \end{align*}
    as $\mathrm{MiPo}_\Q(\omega_q) = \prod_\sigma (\sigma(\omega_q) - X)$.
    Hence, $\alpha$ is not a unit in $\mathcal{O}$.
    On the other hand, $(\alpha)$ is coprime to $(p_i)$ for each $p_i$, as 
    \begin{equation*}
        \omega_q = \alpha - xqP \in (\alpha) + (p_i) \quad \text{and} \quad \omega_q \in \mathcal{O}^\units
    \end{equation*}
    By our assumption, the only prime ideals in $\mathcal{O}$ are the prime ideal factors of $(p_i)$ and $(p)$ for $p \neq p_i$.
    Thus, the prime ideal factorization of $(\alpha)$ consists only of prime ideals $(p), p \neq p_i$ and it follows that $(\alpha) = (n)$ for some integer $n \geq 2$.
    As $\omega_q$ and $xqP \in \Z$ are $\Q$-linearly independent, we see that $n \divides \omega_q$ and $n \divides xqP$.
    However, the former is a contradiction, as $\omega_q \in \mathcal{O}^\units$ is a unit and no $n \geq 2$ is a unit.
\end{proof}
In a later chapter, the book also proves the general result \cite[Chapter VII, Theorem 5.14]{neukirch}.
I am pretty sure that those are exactly the functions $L(s, \chi)$ that we defined above.
\begin{corollary}[Question (iii)]
    There are infinitely many primes $p$ with $p \equiv 1 \pmod 4$.
\end{corollary}
\begin{proof}
    This is just a special case of Prop.~\ref{prop:primes_1_mod_q}.
\end{proof}
\begin{example}[Question (iii)]
    Using a computer, we can also study the actual frequency of prime numbers $\equiv 1, 3 \pmod 4$ among e.g. the first $10^8$ integers.
    This seems to indicate that both numbers are asymptotically equal, which seems natural, given the result of Example~\ref{ex:dirichlet_sum_over_primes}.
    For example, there are 332180 primes $\equiv 1 \pmod 4$ and 332398 primes $\equiv 3$ smaller than $10^8$.
    To find these numbers, the following python code was used.
    \lstinputlisting[language = python]{./primes.py}
\end{example}

@@

    Further, have for $n \in \N$ with $n \perp q$ that $[n] \in (\Z/q\Z)^\units$ and thus
    \begin{equation*}
        [n]^{q - 1} = [n]^{\phi(q)} = [n]^{|(\Z/q\Z)^\units|} = 1 
    \end{equation*}
    As $f$ is a group homomorphism, find
    \begin{equation*}
        \chi(n)^{q - 1} = f([n])^{q - 1} = f([n]^{q - 1}) = f(1) = 1
    \end{equation*}
\end{proof}
This correspondence also works in the other direction.
\begin{corollary}[Question (ii)]
    \label{prop:dirichlet_character_primitive_root}
    Let $\omega \in \C$ be a $(q - 1)$-th root of unity, i.e. $\omega^{q - 1} = 1$ and let $r \in \Z$ be a representative of a primitive root modulo $q$.
    Then
    \begin{equation*}
        g: \N \to \C, \quad n \mapsto \begin{cases}
            \omega^{\log_r n} & \text{if $n \perp q$} \\
            0 & \text{otherwise}
        \end{cases}
    \end{equation*}
    is a well-defined Dirichlet character.
\end{corollary}
\begin{proof}
    Follows again directly from Lemma~\ref{prop:characterization_dirichlet_character}, as $[r] \mapsto \omega$ induces a unique group homomorphism $(\Z/q\Z)^\units \to \C^\units$.
    The associated Dirichlet character is obviously $g$.
\end{proof}
Note that the image of a group homomorphism $f: (\Z/q\Z)^\units \to \C^\units$ is a subgroup of $\C^\units$.
Using Corollary~\ref{prop:dirichlet_character_image_group}, we can describe it quite concretely.
\begin{proposition}
    Let $\chi: \N \to \C$ be a Dirichlet character with group homomorphism $f: (\Z/q\Z)^\units \to \C^\units$.
    Then $\mathrm{im}f \leq S$ is a subgroup where $S_q := \{ \omega_q^k \ | \ k \in \Z \}$ is the group of $q$-th roots of unity.

@@

    Consider a Dirichlet character $\chi \neq \chi_0$ given by $r \mapsto \xi$ for a primitive $q$-th root of unity $\xi \neq 1$.
    Then
    \begin{equation*}
        \sum_{a \in (\Z/q\Z)^\units} \chi(a) = \sum_{k = 0}^{q - 2} \chi(r^k) = \sum_{k = 0}^{q - 2} \xi^k = \frac {1 - \xi^{q - 1}} {q - \xi} = 0 
    \end{equation*}
    By using the earlier results on the structure of $\mathrm{Dir}(q)$ we see that for $a \equiv r^k \not\equiv 1 \pmod q$, have
    \begin{align*}
        \sum_{\chi \in \mathrm{Dir}(q)} \chi(a) &= \sum_{\chi \in \mathrm{Dir}(q)} \chi(r)^k \\
        &= \sum_{\xi \ \text{$q$-th root of unity}} \xi^k = \sum_{l = 0}^{q - 2} \omega^{kl} = \frac {1 - (\omega^{q - 1})^k} {1 - \omega^k} = 0 
    \end{align*}
    where $\omega \in \C$ is any primitive $q$-th root of unity and $r \in \Z$ is a primitive root modulo $q$.

    For the last part, note that for any $q$-th root of unity $\xi$, we have $\xi\overline{\xi} \in \R$ with $\xi\overline{\xi} = |\xi|^2 > 0$.
    Furthermore, $\overline{\xi}$ is also a $q$-th root of unity, and so we see that $\xi\overline{\xi} = 1$ (the only real, positive root of unity is 1).
    It follows that for any Dirichlet character $\chi$ have $\overline{\chi([a])} = \chi([a]^{-1})$.
    Thus
    \begin{equation*}
        \sum_{\chi \in \mathrm{Dir}(q)} \chi(a)\overline{\chi(b)} = \sum_{\chi \in \mathrm{Dir}(q)} \chi([a][b]^{-1}) = \begin{cases}
            q - 1 & \text{if $[a][b]^{-1} = 1 \in (\Z/q\Z)^\units$} \\
            0 & \text{otherwise}
        \end{cases}
    \end{equation*}
    The condition $ab^{-1} = 1$ is equivalent to $a \equiv b \pmod q$, so the claim follows.
\end{proof}
Using these basic results, we can now prove facts on the Dirichlet series of characters.
\begin{proposition}[Question (iv)]
    \label{prop:representation_mangoldt_series_congruent_a}
    Let $a \perp q$. Then for $\Re(s) > 1$ have
    \begin{equation*}
        \sum_{n \equiv a \ (\text{mod} \ q)} \frac {\Lambda(n)} {n^s} = \frac 1 {q - 1} \sum_{\chi \in \mathrm{Dir}(q)} \overline{\chi(a)} \sum_{n \geq 1} \frac {\Lambda(n) \chi(n)} {n^s}
    \end{equation*}
    (All those series obviously converge absolutely since $\Re(s) > 1$)
\end{proposition}
\begin{proof}
    By Prop.~\ref{prop:finite_sums_characters} we have for all $n \in \N$ that
    \begin{equation*}
        \frac 1 {q - 1} \sum_{\chi \in \mathrm{Dir}(q)} \overline{\chi(a)} \chi(n) = \begin{cases}
            1 & \text{if $a \equiv n \pmod q$} \\
            0 & \text{otherwise}
        \end{cases}
    \end{equation*}
    It follows that
    \begin{align*}
        \sum_{n \equiv a \ (\text{mod} \ q)} \Lambda(n) n^{-s} =& \sum_{n \geq 1} \Lambda(n) n^{-s} \begin{cases}
            1 & \text{if $a \equiv n \pmod q$} \\
            0 & \text{otherwise}
        \end{cases} \\
        =& \sum_{n \geq 1} \Lambda(n) n^{-s} \frac 1 {q - 1} \sum_{\chi \in \mathrm{Dir}(q)} \overline{\chi(a)} \chi(n) \\
        =& \frac 1 {q - 1} \sum_{\chi \in \mathrm{Dir}(q)} \overline{\chi(a)} \sum_{n \geq 1} \Lambda(n) \chi(n) n^{-s} 
    \end{align*}
    as infinite summation clearly commutes with finite sums.
\end{proof}
\begin{example}[Question (v)]
    \label{ex:nontrivial_dirichlet_characters_mod_5}
    We consider the Dirichlet characters mod 5.
    A (primitive) 5-th root of unity $\omega_5 \in \C$ is given by $\omega_5 = \exp(2\pi i/5)$.
    On the other hand, a primitive root modulo 5 is e.g. given by $r = 2$ since $2^2 \equiv -1 \pmod 5$.
    Thus we have the trivial Dirichlet character $\chi_0$ and $5 - 1 = 4$ nontrivial Dirichlet characters mod 5, namely those given by
    \begin{align*}
        \chi_1: 1 &\mapsto 1,\ 2 \mapsto \omega_5 = \exp(2\pi i/5),\ 3 \mapsto \omega_5^3 = \exp(6\pi i/5),\ 4 \mapsto \omega_5^2 = \exp(4\pi i/5),\ \\
        \chi_2: 1 &\mapsto 1,\ 2 \mapsto \omega_5^2 = \exp(4\pi i/5),\ 3 \mapsto \omega_5 = \exp(2\pi i/5),\ 4 \mapsto \omega_5^4 = \exp(8\pi i/5),\ \\
        \chi_3: 1 &\mapsto 1,\ 2 \mapsto \omega_5^3 = \exp(6\pi i/5),\ 3 \mapsto \omega_5^4 = \exp(8\pi i/5),\ 4 \mapsto \omega_5^1 = \exp(2\pi i/5),\ \\
        \chi_4: 1 &\mapsto 1,\ 2 \mapsto \omega_5^4 = \exp(8\pi i/5),\ 3 \mapsto \omega_5^2 = \exp(4\pi i/5),\ 4 \mapsto \omega_5^3 = \exp(6\pi i/5),\ \\
    \end{align*}
\end{example}

@@

    The function $L(s, \chi)'/L(s, \chi)$ is bounded on a neighborhood of $1$, provided that $L(1, \chi) \neq 0$.

@@

    However, the derivative of a holomorphic function is again holomorphic, so $L(s, \chi)'$ has no pole at $s = 1$.
    Provided that $L(1, \chi) \neq 0$, it follows that $L(s, \chi)'/L(s, \chi)$ is holomorphic on a compact neighborhood of $1$, so bounded.
\end{proof}
Now we can show the main result of this miniproject.
We will prove two auxiliary lemmas before.
\begin{lemma}
    \label{prop:rho_pole_at_one}
    For $a \perp q$, the function
    \begin{equation*}
        \rho_a(s) := \frac 1 {q - 1} \sum_{\chi \in \mathrm{Dir}(q)} \overline{\chi(a)} \sum_{n \geq 1} \frac {\Lambda(n) \chi(n)} {n^s}
    \end{equation*}
    defined on $\Re(s) > 1$ has a meromorphic continuation to $\Re(s) > 0$ with a simple poles at $1$ (and possibly other poles on $\Re(s) > 0$), provided that $L(1, \chi) \neq 0$ for all $\chi \in \mathrm{Dir}(q) \setminus \{ \chi_0 \}$.
\end{lemma}
\begin{proof}
    By Prop.~\ref{prop:logarithmic_derivative_L}, we have for $\chi \in \mathrm{Dir}(q)$ and $\Re(s) > 1$ that
    \begin{equation*}
        \frac {\overline{\chi(a)}} {q - 1} \sum_{n \geq 1} \frac {\Lambda(n) \chi(n)} {n^s} = \frac {\overline{\chi(a)}} {q - 1} \frac {L(s, \chi)'} {L(s, \chi)}
    \end{equation*}
    Hence
    \begin{equation*}
        \rho_a(s) := \frac 1 {q - 1} \sum_{\chi \in \mathrm{Dir}(q)} \overline{\chi(a)} \frac {L(s, \chi)'} {L(s, \chi)}
    \end{equation*}
    for $\Re(s) > 1$ and the right-hand side is a meromorphic continuation of $\rho_a(s)$ to $\Re(s) > 0$.

>>>>

\title{Miniproject - Analytic Number Theory}
\author{Candidate Number: 1059926}
\date{19.12.2021}

@@

    Note that property (ii) and (iii) directly follow from the definition, as $\chi_f(n)$ only depends on the value of $n$ modulo $q$.
    So consider some $a, b \in \N$.
    If both $a \perp q$ and $b \perp q$ then
    \begin{equation*}
        \chi_f(a)\chi_f(b) = f([a])f([b]) = f([ab]) = \chi_f(ab)
    \end{equation*}
    as also $ab \perp q$.

@@

        \sum_{X \leq n \leq Y} \left| \chi(n) n^{-s} \right| \leq \sum_{X \leq n \leq Y} C \left| n^{-s} \right| \leq C \sum_{X \leq n \leq Y} \left| n^{-s} \right|

@@

        &\geq \sum_{n \geq 0} \ \sum_{0 < k \leq q}\sgn(c) \chi(qn + k) (qn + q)^{-s} \\
        &= \sum_{n \geq 0} \sgn(c) (qn + q)^{-s} \underbrace{\sum_{0 < k \leq q} \chi(qn + k)}_{= c} \\
        &= \frac {|c|} {q^s} \sum_{n \geq 1} n^{-s} = \frac {|c|} {(q + 1)^s} \zeta(s)

@@

        &\leq (qn)^s \frac {sk(qn)^{-1}} {(q^2n^2 + qnk)^s} = \frac {sk} {qn(qn + k)^s} = O(s(qn)^{-s - 1})

@@

    If $s > 1$ and $k \leq q$, then also $(qn)^{-s} - (qn + k)^{-s} = O(s(qn)^{-(1 + \epsilon)})$ for some small enough $0 < \epsilon < 1$.

@@

        =& \ O(qCX^{-s} + qCY^{-s}) + \sum_{X/q \leq n \leq Y/q} \ \sum_{0 < k \leq q} \chi(qn + k) \Bigl( (qn)^{-s} + \underbrace{(qn + k)^{-s} - (qn)^{-s}}_{= O(s(qn)^{-(1 + \epsilon)})} \Bigr) \\
        =& \ O(qCX^{-s}) + \sum_{X/q \leq n \leq Y/q} \Bigl( (qn)^{-s} c + \sum_{0 < k \leq q} O(Cs(qn)^{-(1 + \epsilon)}) \Bigr) = \\
        =& \ O(qCX^{-s}) + 0 + O\Bigl( Cqs \sum_{X/q \leq n \leq Y/q} (qn)^{-(1 + \epsilon)} \Bigr) \\
        =& \ O(qCX^{-s}) + O\Bigl( Cq^{-\epsilon}s \sum_{n \geq X/q} n^{-(1 + \epsilon)} \Bigr)

@@

    Thus the limit is continuous and extends $L(s, \chi)$ defined on $]1, \infty[$.
    It follows that $\lim_{t \to s^+} L(t, \chi)$ exists and is equal to $\sum_{n \geq 1} \chi(n) n^{-s}$.

@@

        \log(1 - x) = -x + O(|x|^2)

@@

    as by Taylor series expansion, find for $|x| < 1$

@@

    Now consider the element $\alpha = \omega_q - xqP \in \mathcal{O}$. Then
    \begin{align*}
        N_{K/\Q}(\alpha) &= \prod_{\sigma: K \to \C \ \text{$\Q$-field homomorphism}} \sigma(\omega_q - xqP) \\
        &= \prod_{\sigma} (\sigma(\omega_q) - xqP) = \mathrm{MiPo}_\Q(\omega_q)(xqP) = \Phi_q(xqP) \neq 1
    \end{align*}
    as $\mathrm{MiPo}_\Q(\omega_q) = \prod_\sigma (\sigma(\omega_q) - X)$.
    Hence, $\alpha$ is not a unit in $\mathcal{O}$.
    On the other hand, $(\alpha)$ is coprime to $(p_i)$ for each $p_i$, as 
    \begin{equation*}
        \omega_q = \alpha - xqP \in (\alpha) + (p_i) \quad \text{and} \quad \omega_q \in \mathcal{O}^\units
    \end{equation*}
    By our assumption, the only prime ideals in $\mathcal{O}$ are the prime ideal factors of $(p_i)$ and $(p)$ for $p \neq p_i$.
    Thus, the prime ideal factorization of $(\alpha)$ consists only of prime ideals $(p), p \neq p_i$ and it follows that $(\alpha) = (n)$ for some integer $n \geq 2$.
    As $\omega_q$ and $xqP \in \Z$ are $\Q$-linearly independent, we see that $n \divides \omega_q$ and $n \divides xqP$.
    However, the former is a contradiction, as $\omega_q \in \mathcal{O}^\units$ is a unit and no $n \geq 2$ is a unit.
\end{proof}
In a later chapter, the book also proves the general result \cite[Chapter VII, Theorem 5.14]{neukirch}.
For this, it uses again the functions $L(s, \chi)$ as introduced here.
\begin{corollary}[Question (iii)]
    There are infinitely many primes $p$ with $p \equiv 1 \pmod 4$.
\end{corollary}
\begin{proof}
    This is just a special case of Prop.~\ref{prop:primes_1_mod_q}.
\end{proof}
\begin{example}[Question (iii)]
    Using a computer, we can also study the actual frequency of prime numbers $\equiv 1, 3 \pmod 4$ among e.g. the first $10^8$ integers.
    This seems to indicate that both numbers are asymptotically equal, which seems natural, given the result of Example~\ref{ex:dirichlet_sum_over_primes}.
    For example, there are 332180 primes $\equiv 1 \pmod 4$ and 332398 primes $\equiv 3$ smaller than $10^8$.
    To find these numbers, the following python code was used.
    \lstinputlisting[language = python]{./primes.py}
\end{example}

@@

    Further, have for $n \in \N$ with $n \perp q$ that $[n] \in (\Z/q\Z)^\units$ and thus
    \begin{equation*}
        [n]^{q - 1} = [n]^{\phi(q)} = [n]^{|(\Z/q\Z)^\units|} = 1 
    \end{equation*}
    As $f$ is a group homomorphism, find
    \begin{equation*}
        \chi(n)^{q - 1} = f([n])^{q - 1} = f([n]^{q - 1}) = f(1) = 1
    \end{equation*}
\end{proof}
This correspondence also works in the other direction.
\begin{corollary}[Question (ii)]
    \label{prop:dirichlet_character_primitive_root}
    Let $\omega \in \C$ be a $(q - 1)$-th root of unity, i.e. $\omega^{q - 1} = 1$ and let $r \in \Z$ be a representative of a primitive root modulo $q$.
    Then
    \begin{equation*}
        g: \N \to \C, \quad n \mapsto \begin{cases}
            \omega^{\log_{[r]} [n]} & \text{if $n \perp q$} \\
            0 & \text{otherwise}
        \end{cases}
    \end{equation*}
    is a well-defined Dirichlet character.
\end{corollary}
\begin{proof}
    Follows again directly from Lemma~\ref{prop:characterization_dirichlet_character}, as $[r] \mapsto \omega$ induces a unique group homomorphism $(\Z/q\Z)^\units \to \C^\units$.
    The associated Dirichlet character is obviously $g$.
\end{proof}
Note that the image of a group homomorphism $f: (\Z/q\Z)^\units \to \C^\units$ is a subgroup of $\C^\units$.
Using Corollary~\ref{prop:dirichlet_character_image_group}, we can describe it quite concretely.
\begin{proposition}
    Let $\chi: \N \to \C$ be a Dirichlet character with group homomorphism $f: (\Z/q\Z)^\units \to \C^\units$.
    Then $\mathrm{im}f \leq S_q$ is a subgroup where $S_q := \{ \omega_q^k \ | \ k \in \Z \}$ is the group of $q$-th roots of unity.

@@

    Consider a Dirichlet character $\chi \neq \chi_0$ given by $r \mapsto \xi$ for a primitive $q$-th root of unity $\xi \neq 1$.
    Then
    \begin{equation*}
        \sum_{a \in (\Z/q\Z)^\units} \chi(a) = \sum_{k = 1}^{q - 1} \chi(r^k) = \sum_{k = 1}^{q - 1} \xi^k = \xi \frac {1 - \xi^{q - 1}} {q - \xi} = 0 
    \end{equation*}
    By using the earlier results on the structure of $\mathrm{Dir}(q)$ we see that for $a \equiv r^k \not\equiv 1 \pmod q$, have
    \begin{align*}
        \sum_{\chi \in \mathrm{Dir}(q)} \chi(a) &= \sum_{\chi \in \mathrm{Dir}(q)} \chi(r)^k \\
        &= \sum_{\xi \ \text{$q$-th root of unity}} \xi^k = \sum_{l = 1}^{q - 1} \omega^{kl} = \omega^{k} \frac {1 - (\omega^{q - 1})^k} {1 - \omega^k} = 0 
    \end{align*}
    where $\omega \in \C$ is any primitive $q$-th root of unity and $r \in \Z$ is a primitive root modulo $q$.

    For the last part, note that for any $q$-th root of unity $\xi$, we have $\xi\overline{\xi} \in \R$ with $\xi\overline{\xi} = |\xi|^2 > 0$.
    Furthermore, $\overline{\xi}$ is also a $q$-th root of unity, and so we see that $\xi\overline{\xi} = 1$ (the only real, positive root of unity is 1).
    It follows that for any Dirichlet character $\chi$ have $\overline{\chi([a])} = \chi([a]^{-1})$.
    Thus
    \begin{equation*}
        \sum_{\chi \in \mathrm{Dir}(q)} \chi(a)\overline{\chi(b)} = \sum_{\chi \in \mathrm{Dir}(q)} \chi([a][b]^{-1}) = \begin{cases}
            q - 1 & \text{if $[a][b]^{-1} = 1 \in (\Z/q\Z)^\units$} \\
            0 & \text{otherwise}
        \end{cases}
    \end{equation*}
    The condition $[a][b]^{-1} = 1$ is equivalent to $a \equiv b \pmod q$, so the claim follows.
\end{proof}
Using these basic results, we can now prove facts on the Dirichlet series of characters.
\begin{proposition}[Question (iv)]
    \label{prop:representation_mangoldt_series_congruent_a}
    Let $a \perp q$. Then for $\Re(s) > 1$ have
    \begin{equation*}
        \sum_{n \equiv a \ (\text{mod} \ q)} \frac {\Lambda(n)} {n^s} = \frac 1 {q - 1} \sum_{\chi \in \mathrm{Dir}(q)} \overline{\chi(a)} \sum_{n \geq 1} \frac {\Lambda(n) \chi(n)} {n^s}
    \end{equation*}
    (All those series obviously converge absolutely since $\Re(s) > 1$)
\end{proposition}
\begin{proof}
    By Prop.~\ref{prop:finite_sums_characters} we have for all $n \in \N$ that
    \begin{equation*}
        \frac 1 {q - 1} \sum_{\chi \in \mathrm{Dir}(q)} \overline{\chi(a)} \chi(n) = \begin{cases}
            1 & \text{if $a \equiv n \pmod q$} \\
            0 & \text{otherwise}
        \end{cases}
    \end{equation*}
    It follows that
    \begin{align*}
        \sum_{n \equiv a \ (\text{mod} \ q)} \Lambda(n) n^{-s} =& \sum_{n \geq 1} \Lambda(n) n^{-s} \begin{cases}
            1 & \text{if $a \equiv n \pmod q$} \\
            0 & \text{otherwise}
        \end{cases} \\
        =& \sum_{n \geq 1} \Lambda(n) n^{-s} \frac 1 {q - 1} \sum_{\chi \in \mathrm{Dir}(q)} \overline{\chi(a)} \chi(n) \\
        =& \frac 1 {q - 1} \sum_{\chi \in \mathrm{Dir}(q)} \overline{\chi(a)} \sum_{n \geq 1} \Lambda(n) \chi(n) n^{-s} 
    \end{align*}
    as infinite summation clearly commutes with finite sums.
\end{proof}
\begin{example}[Question (v)]
    \label{ex:nontrivial_dirichlet_characters_mod_5}
    We consider the Dirichlet characters mod 5.
    A (primitive) 5-th root of unity $\omega_5 \in \C$ is given by $\omega_5 = \exp(2\pi i/5)$.
    On the other hand, a primitive root modulo 5 is e.g. given by $r = 2$ since $2^2 \equiv -1 \pmod 5$.
    Thus we have the trivial Dirichlet character $\chi_0$ and $5 - 1 = 4$ nontrivial Dirichlet characters mod 5, namely those given by
    \begin{align*}
        \chi_1: 1 &\mapsto 1,\ 2 \mapsto \omega_5 = \exp(2\pi i/5),\ 3 \mapsto \omega_5^3 = \exp(6\pi i/5),\ 4 \mapsto \omega_5^2 = \exp(4\pi i/5),\ \\
        \chi_2: 1 &\mapsto 1,\ 2 \mapsto \omega_5^2 = \exp(4\pi i/5),\ 3 \mapsto \omega_5 = \exp(2\pi i/5),\ 4 \mapsto \omega_5^4 = \exp(8\pi i/5),\ \\
        \chi_3: 1 &\mapsto 1,\ 2 \mapsto \omega_5^3 = \exp(6\pi i/5),\ 3 \mapsto \omega_5^4 = \exp(8\pi i/5),\ 4 \mapsto \omega_5^1 = \exp(2\pi i/5),\ \\
        \chi_4: 1 &\mapsto 1,\ 2 \mapsto \omega_5^4 = \exp(8\pi i/5),\ 3 \mapsto \omega_5^2 = \exp(4\pi i/5),\ 4 \mapsto \omega_5^3 = \exp(6\pi i/5),\ \\
    \end{align*}
\end{example}

@@

    Let $\chi \neq \chi_0$ be a Dirichlet character modulo $q$.
    Then the function $L(s, \chi)'/L(s, \chi)$ is bounded on a neighborhood of $1$, provided that $L(1, \chi) \neq 0$.

@@

    However, the derivative of a holomorphic function is again holomorphic, so $L(s, \chi)'$ has no pole at $s = 1$ (since we know that $L(s, \chi)$ has not pole at $s = 1$ for $\chi \neq \chi_0$).
    Provided that $L(1, \chi) \neq 0$, it follows that $L(s, \chi)'/L(s, \chi)$ is holomorphic on a compact neighborhood of $1$, so bounded.
\end{proof}
Now we can show the main result of this miniproject.
We will prove two auxiliary lemmas before.
\begin{lemma}
    \label{prop:rho_pole_at_one}
    For $a \perp q$, the function
    \begin{equation*}
        \rho_a(s) := \frac 1 {q - 1} \sum_{\chi \in \mathrm{Dir}(q)} \overline{\chi(a)} \sum_{n \geq 1} \frac {\Lambda(n) \chi(n)} {n^s}
    \end{equation*}
    defined on $\Re(s) > 1$ has a meromorphic continuation to $\Re(s) > 0$ with a simple poles at $1$ (and possibly other poles on $\Re(s) > 0$), provided that $L(1, \chi) \neq 0$ for all $\chi \in \mathrm{Dir}(q) \setminus \{ \chi_0 \}$.
\end{lemma}
\begin{proof}
    By Prop.~\ref{prop:logarithmic_derivative_L}, we have for $\chi \in \mathrm{Dir}(q)$ and $\Re(s) > 1$ that
    \begin{equation*}
        \frac {\overline{\chi(a)}} {q - 1} \sum_{n \geq 1} \frac {\Lambda(n) \chi(n)} {n^s} = \frac {\overline{\chi(a)}} {q - 1} \frac {L(s, \chi)'} {L(s, \chi)}
    \end{equation*}
    Hence
    \begin{equation*}
        \rho_a(s) := \frac 1 {q - 1} \sum_{\chi \in \mathrm{Dir}(q)} \overline{\chi(a)} \frac {L(s, \chi)'} {L(s, \chi)}
    \end{equation*}
    for $\Re(s) > 1$ and the right-hand side is a meromorphic continuation of $\rho_a(s)$ to $\Re(s) > 0$.
